This is the Title

### 2017-03-16 trunk/abc/paper/paper.tex
Add weird histo idea

TODO: X86 vs x86

@@

(Idea: Once we've gone past EIP=0xFFFF, we can still execute code from our binary.
It may be possible to get back to CS by doing a jump with the address/operand size prefix?
Neither one has an effect in DOSBox, which may be a bug? Anyway, if an interrupt
is triggered while we're up here, it seems like it only does a 16-bit RET, so that's
kinda busted.)

@@

songs to do: https://www.youtube.com/watch?v=EJkJbUbvYJA

@@

XXX: Should really write about PSP.
could write about optimizing the value table

>>>>

TODO: X86 vs x86
TODO: make sure to ctrl-u meta-q every paragraph

@@

@@

songs to do: https://www.youtube.com/watch?v=EJkJbUbvYJA
 - mario theme.

@@

could write about optimizing the value table
